---
title: "Alexander Durbin"
output: 
  flexdashboard::flex_dashboard:
    theme: lumen
    social: ["menu"]
    source_code: embed
runtime: shiny
---

About {.sidebar}
=====================================  

I am a second-year graduate student in the Department of Statistics at Virginia Tech. I graduated from Michigan State University in May, 2016 with a B.S. in mathematics. 

<i class="fa fa-external-link"></i> https://www.myhomepage.com

<i class="fa fa-envelope"></i> me@myemail.com

Home {data-icon="fa-home"}
=====================================  
    
Column {data-width=600}
-------------------------------------
    
### Chart 1
    
```{r}
shinyAppDir(
  system.file("examples/11_timer", package="shiny"),
  options = list(height=850)
)
```

Column {data-width=400}
-------------------------------------
   
### Chart 2

```{r}
shinyAppDir(
  system.file("examples/02_text", package="shiny"),
  options = list(height=850)
)
```   
 
### Chart 3
    
```{r}
shinyAppDir(
  system.file("examples/03_reactivity", package="shiny"),
  options = list(height=850)
)
```

CV {data-orientation=rows, data-icon="fa-file"}
=====================================     
   
Row {data-height=600}
-------------------------------------

### Chart 1

```{r}
shinyAppDir(
  system.file("examples/07_widgets", package="shiny"),
  options = list(height=850)
)
```

Row {data-height=400}
-------------------------------------
   
### Chart 2

```{r}
shinyAppDir(
  system.file("examples/05_sliders", package="shiny"),
  options = list(height=850)
)
```   


### Chart 3

```{r}
shinyAppDir(
  system.file("examples/04_mpg", package="shiny"),
  options = list(height=850)
)
```
    

R Shiny {data-icon="fa-code"}
=====================================

```{r}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options = list(height=850)
)
```

Tabset
=====================================   

Column {.tabset}
-------------------------------------
   
### Chart 2

```{r}
shinyAppDir(
  system.file("examples/09_upload", package="shiny"),
  options = list(height=850)
)
```   
 
### Chart 3
    
```{r}
shinyAppDir(
  system.file("examples/10_download", package="shiny"),
  options = list(height=850)
)
```


More Shiny
===================================== 
```{r}
shinyAppDir(
  system.file("examples/01_hello", package="shiny"),
  options = list(height=850)
)
```
